---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pakete: Utilities for Package Development

<!-- badges: start -->
<!-- badges: end -->

Tools and utilities for package development currently not available from usual development tools. These are mostly linked to personal preferences during the development process. They assist in making routine and repetitive tasks easily implementable.

## What does `pakete` do?

Currently, `pakete` includes functions for:

1. creating GitHub checklists for tasks in the package submission process;

2. creating `_pkgdown.yml` templates for projects that I work on;

3. creating line snippets for `DESCRIPTION` file;

## Installation

You can install `pakete` via the [Katilingban R-universe](https://katilingban.r-universe.dev) as follows:

```{r install-r-universe, eval = FALSE}
install.packages(
  "pakete",
  repos = c('https://katilingban.r-universe.dev', 'https://cloud.r-project.org')
)
```

## Usage

## Citation

## Community guidelines

Feedback, bug reports and feature requests are welcome; file issues or seek support [here](https://github.com/katilingban/pakete/issues). If you would like to contribute to the package, please see our [contributing guidelines](https://katilingban.io/pakete/CONTRIBUTING.html).

Please note that the `paketa` project is released with a [Contributor Code of Conduct](https://katilingban.io/pakete/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

